Algebraic File Synchronization: Adequacy and Completeness

### 2017-09-30 p2/ordering.tex
Improved intro to ordering

Let us therefore define $\ordersetsign$ which gives all
permutations of a set of commands that do not break all filesystems.

\begin{mydef}[$\ordersetsign$]\label{def_orderset}
For a simple set or sequence of commands $U$,
we use $\orderset{U}$ to denote the set of sequences
that are all permutations of the commands in $U$
for which the following holds:
for all subsequences $\cxynv\cc\czwmv$,
\begin{itemize}
\item if $n=\parent(m)$, then $y=\vald$
\item if $\parent(n)=m$, then $y=\empt$.
\end{itemize}
\end{mydef}

@@

In \cref{simple_reorder_equiv} we offer a formal proof that 
$\orderset{U}$ contains all possible permutations.
It is an important property of simple sequences: namely, that
all of their valid reorderings are equivalent,
and all equivalent sequences are mere reorderings.
To prove this, we will need the following results.

@@

For the proof we define construction and descruction commands as follows:
\begin{mydef}[Construction command]
A command $\cxynv$ is a construction command if it can appear in a construction pair,
that is, if $[x]=[\empt]$ and $[y]\neq[\empt]$,
or if $[x]=[\valf]$ and $[y]=[\vald]$.
\end{mydef}
\begin{mydef}[Destruction command]
A command $\cxynv$ is a destruction command if it can appear in a destruction pair,
that is, 
if $[x]=[\valf]$ and $[y]=[\empt]$,
or if $[x]=[\vald]$ and $[y]\neq[\vald]$.
Note that a command cannot be both a construction and a destruction command.
\end{mydef}

>>>>

We recognize that mulitple orders may be possible;
let us therefore describe our ordering algorithm by
defining a subset of the permutations, $\ordersetsign$.
The simplicity of the definition means that enumerating
all sequences in $\ordersetsign$ can be implemented by a straightforward
algorithm.

As we will see, $\ordersetsign$ generates all possible
sequences of commands that do not break all filesystems.
In \cref{simple_reorder_equiv}, we offer a formal proof of this.
It is an important property of simple sequences: namely, that
all of their valid reorderings are equivalent,
and all equivalent sequences are mere reorderings.

\begin{mydef}[$\ordersetsign$]\label{def_orderset}
For a simple set or sequence of commands $S$,
we use $\orderset{S}$ to denote the set of sequences
that are all permutations of the commands in $S$
for which the following holds:
for all subsequences $\cxynv\cc\czwmv$,
\begin{itemize}
\item if $n=\parent(m)$, then $y=\vald$
\item if $\parent(n)=m$, then $y=\empt$.
\end{itemize}
\end{mydef}

@@

To prove \cref{simple_reorder_equiv}, we need the following results.

@@

% TODO APPENDIX
For the proof we define construction and descruction commands as follows:
\begin{mydef}[Construction command]
A command $\cxynv$ is a construction command if it can appear in a construction pair,
that is, if $[x]=[\empt]$ and $[y]\neq[\empt]$,
or if $[x]=[\valf]$ and $[y]=[\vald]$.
\end{mydef}
\begin{mydef}[Destruction command]
A command $\cxynv$ is a destruction command if it can appear in a destruction pair,
that is, 
if $[x]=[\valf]$ and $[y]=[\empt]$,
or if $[x]=[\vald]$ and $[y]\neq[\vald]$.
Note that a command cannot be both a construction and a destruction command.
\end{mydef}
